\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
\usepackage[scale=0.75]{geometry}

% Uniform name formatting
\newcommand{\myname}{\textbf{\textsc{Shubham Mane}}} % Single font command

% Personal info
\name{\myname}{}
\address{Chicago, IL 60613}
\phone[mobile]{312-539-9755}
\email{shubhammane56@gmail.com}
\homepage{linkedin.com/in/shubhmane}


\begin{document}
\makecvtitle

% Summary
\section{Professional Summary}
Senior Security Analyst with 8+ years of experience leading complex security assessments, penetration testing, and incident response initiatives across enterprise environments. Proven expertise in applying NIST cybersecurity frameworks, managing robust vulnerability management programs, and optimizing SIEM solutions to reduce response time and improve threat detection. Adept at mentoring junior analysts, developing security policies, and collaborating cross-functionally to embed security best practices throughout the organization. Skilled in forensic investigations, threat intelligence, and cloud security with hands-on experience in scripting and automation.

\section{Technical Skills}
\cvitem{Networking}{Packet Analysis (tcpdump, Wireshark), IDS (Bro, Snort), Splunk, Firewall, IDS/IPS, Access Control}
\cvitem{Systems Administration}{Active Directory, DNS, FTP, SSH, DHCP, SMB, HTTP, Virtualization}
\cvitem{Vulnerability Assessment}{Nmap, Nessus, Ettercap, Qualys, Metasploit, Honeypots (honeyD, inetSim), BurpSuite, Nexpose, Acunetix, IBM App Scan, HP Web Inspect}
\cvitem{End Point Security}{FortiNet, McAfee Suites (VSE, HIPS \& HDLP), McAfee MOVE AV, Symantec, McAfee Email Security Gateways (GUI \& CLI), McAfee Network DLP, McAfee NITRO SIEM, Cisco Security (AMP, Umbrella, Email Security), FireEye HX}
\cvitem{Platforms \& Applications}{Continuous Monitoring, Vulnerability Management, Web Application Scanning, ThreatProtect, Policy Compliance, Cloud Agents, Asset Management}
\cvitem{Security Software}{Nessus, Nmap, Metasploit, Snort, RSA Authentication, PIA, Demisto, CrowdStrike, CyberArk}
\cvitem{Programming Languages}{C, C++, Java, Python, JavaScript, PowerShell, Linux}
\cvitem{Domain Knowledge}{Risk Management, BCP/DRP, ISO 27001, COBIT, SWOT Analysis, Cryptography, Incident Response, Penetration Testing, Risk Assessment, SCADA Security, SCADA Audits, SIEM, ITIL, NIST, FIPS}
\cvitem{Tools}{Burp Suite, Wireshark, WebScarab, Nmap, Metasploit, SQLMap, OWASP ZAP Proxy}
\cvitem{Web App Vulnerability Scanning}{Nessus, OpenVAS, HP WebInspect, IBM AppScan, Tenable.io}
\cvitem{Web Application Security}{Manual SQL Injection, Manual Cross-Site Scripting (XSS), Cross-Site Request Forgery (CSRF), SQLMap}

% Experience
\section{Professional Experience}

\cventry{Jun 2022--Present}{Senior Security Specialist}{Client: Verizon}{Chicago, IL}{}{
\begin{itemize}
\item Developed and implemented threat intelligence products that matched organizational requirements and priorities.
\item Monitored and analyzed threat intelligence data to identify emerging threats and attack vectors.
\item Successfully managed high-priority security incidents, coordinating with cross-functional teams to contain and resolve threats with minimal downtime.
\item Developed incident escalation procedures, ensuring timely notification and resolution of critical security events.
\item Led complex security assessments involving penetration testing, vulnerability scanning, and risk assessments to identify and remediate critical security gaps, improving overall security posture by 30\%.
\item Conducted comprehensive penetration tests simulating real-world threat scenarios, resulting in the discovery and mitigation of high-impact vulnerabilities across enterprise environments.
\item Designed and deployed AI-powered tools to strengthen cybersecurity across diverse platforms.
\item Integrated AI-driven automation for proactive threat detection and response systems.
\item Built ML models to identify malicious behavior and enhance incident response workflows.
\item Applied secure design principles to AI integrations across DevSecOps environments.
\item Ensured secure implementation of MyCity chatbot features through rigorous AI validation.
\end{itemize}
}

\medskip

\cventry{Oct 2021--Jun 2022}{Cyber Security Analyst}{Client: AT\&T}{Pittsburg, PA}{}{
\begin{itemize}
\item Analyzed threat intelligence data to identify common and emerging attack vectors and penetration methods.
\item Collaborated with business leaders and IT teams to design security solutions that protect sensitive data without disrupting business operations.
\item Translated complex security risks into business-impact statements, helping non-technical stakeholders understand security priorities.
\item Applied strong working knowledge of ISO 27001 LA/LI certification requirements to design effective control frameworks and lead audit engagements.
\item Assessed security risks across multi-tenant cloud environments, ensuring compliance with data protection regulations and cloud-specific security frameworks.
\item Automated test case execution using Python frameworks for functional and regression testing.
\item Conducted usability and performance testing for AI algorithms in production environments.
\item Created and maintained test scripts to validate machine learning models.
\item Evaluated AI model behavior through robust testing and anomaly detection protocols.
\item Built REST API-based automation workflows to test and monitor threat management tools.
\item Contributed to threat management operations by engineering custom security alerts.
\item Developed security rules and detection logic for enterprise-level cybersecurity tools.
\item Supported incident response teams with ML-based log analysis and alert correlation.
\item Strengthened detection capabilities through API integrations with Cyber Command systems.
\item Engineered response orchestration logic to streamline alert triaging.
\end{itemize}
}

\medskip

\cventry{Jun 2018--Aug 2021}{Information Security Engineer}{INFOSYS Ltd.}{India}{}{
\begin{itemize}
\item Implemented and managed cybersecurity technologies and strategies, including the MITRE ATT\&CK framework and incident response procedures.
\item Conducted threat intelligence and analytics to identify and mitigate security risks.
\item Managed Git-based development lifecycle for secure code deployment.
\item Documented code, automation logic, and process flows for secure platform operations.
\item Enhanced alert accuracy by integrating external threat intel sources into SOC tooling.
\item Implemented cloud-native security controls on Azure and AWS platforms.
\end{itemize}
}

\medskip

\cventry{Jan 2017--May 2018}{Infrastructure Security Analyst}{Icertis}{India}{}{
\begin{itemize}
\item Monitored and analyzed security logs and alerts to identify potential threats and vulnerabilities.
\item Conducted penetration testing and vulnerability assessments to evaluate the effectiveness of security controls.
\item Developed and implemented security processes and procedures to enhance the overall security posture.
\item Worked with cross-functional teams to address security incidents and provide recommendations for remediation.
\item Maintained up-to-date knowledge of common and emerging attack vectors and countermeasures.
\end{itemize}
}

% Certifications
\section{Certifications}
\cvlistitem{\textbf{Certified Ethical Hacker (CEH)}}
\cvlistitem{\textbf{AWS Certified Solutions Architect}}
\cvlistitem{\textbf{CompTIA Security+}}

% Education
\section{Education}
\cventry{2021}{Master of Science in Cyber Security}{DePaul University}{Chicago, IL}{}{}
\cventry{2017}{Bachelor of Engineering in Computer Science}{Dr. D.Y. Patil Institute of Technology, Pimpri}{Pune, India}{}{}



\end{document}
